A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

\subsubsection{Understanding the principal component spaces}\label{subsubsection:visualization_pcspaces}
Essentially, the existing permeability space is transformed (with SVD and HOSVD for 2- and 3-D permeability fields, respectively) to principal component spaces (PCS). Within the PCS, traditional PCA dimensionality reduction can be optionally performed (\ie{feature selection or elimination}, see Section~\ref{subsubsection:pca_dimred_linreg} for more details), before interpolation is used to implement further data reduction in the principal component spaces. The reduced data in the PCS is then transformed back into the permeability space to obtain a reduced permeability space. An algorithm which impliments the procedure described here, is presented in Section~\ref{subsubsection:svdcase_preprocess_algorithm}

>>>>

\subsubsection{Understanding the principal component spaces}\label{subsubsection:visualization_pcspaces}
Essentially, the existing permeability space is transformed (with SVD and HOSVD for 2- and 3-D permeability data, respectively) to principal component spaces (PCS). Within the PCS, traditional PCA dimensionality reduction can be optionally performed (\ie{feature selection or elimination}, see Section~\ref{subsubsection:pca_dimred_linreg} for more details), before interpolation is used to implement further data reduction in the principal component spaces. The reduced data in the PCS is then transformed back into the permeability space to obtain a reduced permeability space. An algorithm which impliments the procedure described here, is presented in Section~\ref{subsubsection:svdcase_preprocess_algorithm}
